---
title: "p8105_hw1_zq2209"
author: "Zining Qi"
date: "2022-09-21"
output: github_document
---
```{r}
library(tidyverse)
```


# Problem 1
```{r}
data("penguins", package = "palmerpenguins")
```

```{r}
# Getting information about data
summary(penguins)
ncol(penguins)
nrow(penguins)
```

The dataset contains 8 variables, which are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year. Species, island and sex are qualitative variables. Others are quantitative variables. Species, island, bill length, bill depth, flipper length and body mass are meaningful variables that could be explored further, such as the relationship between mass and flip length.

The size of the dataset is 344 rows by 8 columns, 344 X 8.

The mean for flipper length is 200.9mm. 

```{r}
# Scatter plot of flipper length and bill length.
scatterplot_penguins = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, col = species)) + geom_point()
scatterplot_penguins
ggsave("scatterplot_penguins.pdf", plot = scatterplot_penguins)
```



# Problem 2

```{r}
# Creating the data frame
set.seed(1)
df2 = tibble(normal_vec = rnorm(10),
             logic_vec = normal_vec > 0,
             char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
             factor_vec = factor(c("A", "B", "C", "A", "A", "B", "B", "B", "C", "C"))
)
df2
summary(df2)
```

```{r}
# Taking mean for each vector
normal_vec = pull(df2, 1)
logic_vec = pull(df2, 2)
char_vec = pull(df2, 3)
factor_vec = pull(df2, 4)
mean(normal_vec)
mean(logic_vec)
mean(char_vec)
mean(factor_vec)
```

For normal vector, the mean is 0.132. The mean for logic vector is greater or equal to 0, which depends on the number of positive numbers. And there are warning message when tries to get the mean for character vector and factor vector. Because it is impossible to get mean for text(A, B, and so on). 

```{r, eval = FALSE}
# Converting non-numeric variables to numeric numbers
as.numeric(logic_vec)
as.numeric(char_vec)
as.numeric(factor_vec)
```

The number of logic vector doesn't change, but the type changes from logic number to numeric variable. After changing the type of character vector, the value becomes to NA. This means it is unable to assign number to this variable. For factor number, the value change to 1,2,3. This means there are three levels, each number assign a level number. This actually explains why message error occurs listed above. It is impossible to take mean for character, which even can't assign numbers to it, and factors, which although could assign numbers, it doesn't make any sense to take means for different levels.




